The Neuro Bureau ADHD-200 Preprocessed Repository

### 2016-05-14 Bellec_ADHD200_2016.tex
A bit of work on the Oxford commas, and fix to point 4 of reviewer 2 (missing "and" l. 31-32).

In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}. The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}. The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}. Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld. The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise. These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods or access to high performance computing resources. Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.

The ``ADHD-200 Preprocessed'' is a repository of preprocessed rs-fMRI and s-MRI data along with statistical derivatives from the ADHD-200 Sample. Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'' and ``NIAK'') that differed in the toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated. The Athena pipeline processed rs-fMRI and s-MRI images using a combination of AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits. The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry. The NIAK pipeline processed rs-fMRI and s-MRI using the NeuroImaging Analysis Kit \cite{Bellec2011}.

@@

The ADHD-200 Preprocessed data was released in 2011 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}. No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account. This registration enables downloads to be tracked for usage statistics users to be contacted in the event that errors are found in the dataset. The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/ADHD-200/}}. There are no more restrictions placed on the preprocessed data or derivatives other than the request that the ADHD-200 Preprocessed Initiative is cited appropriately and that the specific pipeline is acknowledged in publications using the data. A forum is available on the Neuro Bureau's NITRC project page for users to ask questions or report problems\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=2046}}. Questions regarding data acquisition or phenotypic variables should be directed to INDI's support forum\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=1735}}.

>>>>

In 2011, the ``ADHD-200 Global Competition'' was held with the aim of engaging researchers from a variety of analytical backgrounds to identify biomarkers of attention-deficit/hyperactivity disorder (ADHD) from resting-state functional magnetic resonance imaging (rs-fMRI) and structural MRI (s-MRI) data \cite{Milham2012}. The competition made use of the ``ADHD-200 Sample'' data collection that was aggregated from eight independent sites and shared through the Intenational Neuroimaging Datasharing Initiative (INDI) \cite{Mennes2013}. The data includes rs-fMRI, structural MRI (s-MRI), and basic phenotypic information for 973 individuals (585 typically-developing controls (TDC), 362 ADHD, 26 unknown) \cite{Milham2012}. Competitors were given five and a half months to optimize a classification algorithm on training data (776 individuals) and submit their predicted clinical labels on test data for which diagnostic information was withheld. The competition data was distributed in a raw form and, before any analysis could begin, the images had to be preprocessed to make them comparable across individuals and reduce noise. These preprocessing steps present a significant hurdle for would-be competitors who do not have the specialist knowledge of neuroimaging methods, or access to high performance computing resources. Realizing this barrier to entry, the Neuro Bureau prospectively collaborated with all competitors by preprocessing the data and sharing these results.

The ``ADHD-200 Preprocessed'' is a repository of preprocessed rs-fMRI and s-MRI data along with statistical derivatives from the ADHD-200 Sample. Rather than favoring a specific processing strategy, we followed a pluralistic approach by preprocessing the data using multiple pipelines (called ``Athena'', ``Burner'', and ``NIAK'') that differed in the toolsets used, the philosophy motivating choices of algorithms and parameters, and the statistical derivatives calculated. The Athena pipeline processed rs-fMRI and s-MRI images using a combination of AFNI \cite{cox1996afni} and FSL \cite{smith2004advances} neuroimaging toolkits. The Burner pipeline used SPM8 \cite{ashburner2012spm8} to process s-MRI data for voxel-based morphometry. The NIAK pipeline processed rs-fMRI and s-MRI using the NeuroImaging Analysis Kit \cite{Bellec2011}.

@@

The ADHD-200 Preprocessed data was released in 2011 and can be downloaded from NITRC\footnote{\url{http://www.nitrc.org/frs/?group_id=383}}. No data usage agreement is required to access or download the data, the only requirement is registering for a free NITRC account. This registration enables downloads to be tracked for usage statistics and users to be contacted in the event that errors are found in the dataset. The ADHD-200 Sample allows unrestricted data usage for non-commercial research purposes provided that the specific datasets included in an analysis be cited appropriately and that their funding sources be acknowledged\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/ADHD-200/}}. There are no more restrictions placed on the preprocessed data or derivatives other than the request that the ADHD-200 Preprocessed Initiative is cited appropriately and that the specific pipeline is acknowledged in publications using the data. A forum is available on the Neuro Bureau's NITRC project page for users to ask questions or report problems\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=2046}}. Questions regarding data acquisition or phenotypic variables should be directed to INDI's support forum\footnote{\url{http://www.nitrc.org/forum/forum.php?forum_id=1735}}.
